---
output:
  md_document:
    variant: markdown_github
---

# Intro

This R package was built in STAT545 at UBC, and is intended for teaching/learning purposes only

# Install

This R package can be installed from github:

* Note I haven't pushed the final version yet; will update README when I push the final version

```{r}
#install.package("devtools")
devtools::install_github("margotgunning/powers")
```


# Here's a short example

This can also be seen in the vignette, which I also haven't finished yet

```{r}
powers::square(2)
#>[1] 4

powers::cube(9)
#>[1] 729

powers::box_cox_transform(2,-1)
#>[1] 0.5

powers::inverse_box_cox_transform(0.5,-1)
#>[1] 2
```

# For development

Not much to say here because this is a learning tool.

There is an internal function called pow that is the machinery for the sqaure function, and cube function.

The box-cox transformation functions do not use the internal function pow.  Something else I wanted to look at was adding in a condition to make a dataframe in the input for response and t_params had lenghts greater than one; but I did not have time to do this.

