---
title: "Powers"
author: "Me"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Powers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Intro

This R package was built in STAT545 at UBC, and is intended for teaching/learning purposes only

The main goal of this R package is to compute power and logarithmic transformations without having to use ```^``` or ```**```

# Functions

There are four functions in this package:
	+ ```square```:
		+ input: value to be squared
		+ output: squared value
	+ ```cube```:
		+ input: value to be cubed
		+ output: cubed value
	+ ```box_cox_transform```:
		+ input: response to be transformed; transformation parameter
		+ output: transfromed response
	+ ```inverse_box_cox_transfrom```:
		+ input: transfromed response to be undone; transformation parameter
		+ output: raw response

# Example execution

```{r}
library(powers)
square(2, plot_it=FALSE)
#>[1] 4
cube(3, plot_it=FALSE)
#>[1] 9

box_cox_transform(2, 0.5)
#>[1] 0.8284271
box_cox_transform(2, 0)
#>[1] 0.6931472

inverse_box_cox_transform(0.8284271, 0.5)
#>[1] 2
inverse_box_cox_transform(0.6931472, 0)
#>[1] 2
```

## We can apply powers in lists of vectors too!

```{r}
listy_list <- list(4,2,9,0.2,-0.8,-0.4)
sapply(listy_list, square)
#>[1] 16.00, 4.00, 81.00, 0.04, 0.64, 0.16

lapply(listy_list, box_cox_transform, t_param=0.5)
#[[1]]
#[1] 2

#[[2]]
#[1] 0.8284271

#[[3]]
#[1] 4

#[[4]]
#[1] -1.105573

#[[5]]
#[1] "Number not real, check input"

#[[6]]
#[1] "Number not real, check input"


```

And That's All Folks
